Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/sims.tex
some corrections

% simulations
We use simulations to provide additional evidence for theoretical claims and gain insight into audit behavior. As in \cite{sims}, we use margins from the 2020 US Presidential election, state-wide pairwise margins between the leading two candidates of 5\% or more. Narrower margins are computationally expensive, especially for the simulations with an underyling tie which quickly increase in sample size. We use the simulator in the R2B2 software library\cite{r2b2}. We perform $10000=10^4$ trials per margin for both an underyling announced outcomes and an underyling tie.

The simulations with an underlying tie give an estimate of maximum risk as shown in Figure~\ref{fig:prov-risk}. For all margins, the estimated risks were less than the risk limit.

Simulations with the underlying ballot distribution as announced provide insight into stopping probability and number of ballots drawn. Figure~\ref{fig:prov-sprob} shows that the stoping probabilities over the first rounds are near and slightly above $90\%$ as expected, since our software chose round sizes to give at least a $90\%$ conditional stopping probability.
Figure~\ref{fig:prov-asn} shows that the probability of stopping as a function of number of ballots sampled. Points above (higher probability of stopping) and to the left (fewer ballots) represent more efficient audits. As shown, \Providence has comparable efficiency to \Minerva, while both are significantly more efficient than either implementation of \BRAVO. Note that a difference in twice as many ballots could be negligible in a contest with a wide margin. In a contest with a narrow margin (in the 2020 US Presidential election, several states had margins less than $3\%$) the difference in number of ballots sampled could be weeks of work. Section~\ref{sec:workload} discusses workload in more depth.
%TODO add a more specific number of states for small margin

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_risk.png}
\caption{The proportion of simulated audits with an underlying tie that stopped in one of the five simulated rounds.}
\label{fig:prov-risk}
\end{figure}

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_sprob.png}
\caption{The proportion of simulated audits with an margin as announced that stopped in one of the five simulated rounds.}
\label{fig:prov-sprob}
\end{figure}

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_asn.png}
\caption{For all five rounds, the estimated stopping probability for average number of ballots drawn for \Providence, \Minerva, EoR \BRAVO, and SO \BRAVO.}
\label{fig:prov-asn}
\end{figure}

>>>>

% simulations
We use simulations to provide additional evidence for theoretical claims and gain insight into audit behavior. As in \cite{simulations}, we use margins from the 2020 US Presidential election---state-wide pairwise margins between the leading two candidates of 5\% or more. Narrower margins are computationally expensive, especially for the simulations with an underyling tie, which, by design, have a low probability of stopping and hence require all rounds and quickly increase in sample size. We use the simulator in the R2B2 software library\cite{r2b2}. For each margin, for each hypothesis, we perform $10^4$ trials. RISK LIMIT. NUMBER OF ROUNDS. STOPPING PROB.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_risk.png}
\caption{The fraction of simulated \Providence audits on tied elections that stopped in any rounds (we performed five rounds AT WHAT STOPPING PROB? RISK LIMIT?). This value is an estimate of the maximum risk of the \Providence audit.}
\label{fig:prov-risk}
\end{figure}

In the simulations of \Providence audits of a tied election, the fraction of audits that stop, as shown in Figure~\ref{fig:prov-risk}, is an estimate of maximum risk. For all margins, this estimated maximum risk is less than the risk limit, supporting the claim that \Providence is risk-limiting.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_sprob.png}
\caption{The fraction of simulated \Providence audits of the election as announced that stopped for each round. This value is an estimate of the stopping probability conditioned on the sample of the previous round. The average fraction for rounds 1, 2, and 3 is $89.96\%$, $90.52\%$, and $90.98\%$ respectively. We show only the first three rounds since so few audits make it to rounds 4 and 5.}
\label{fig:prov-sprob}
\end{figure}

Simulations of audits of the election as announced provide insight into stopping probability and number of ballots drawn when the election is as announced. We wish the stopping probability to be as predicted, and the number of ballots drawn to be small. Figure~\ref{fig:prov-sprob} shows that the stopping probabilities over the first rounds are near and slightly above $90\%$ as expected since our software chose round sizes to give at least a $90\%$ conditional stopping probability.

Figure~\ref{fig:prov-asn} plots the probability of stopping as a function of the number of ballots sampled. Points above (higher probability of stopping) and to the left (fewer ballots) represent more efficient audits. As shown, \Providence has comparable efficiency to \Minerva, while both are significantly more efficient than either implementation of \BRAVO. In a contest with a narrow margin (in the 2020 US Presidential election, eight states had margins less than $3\%$) the difference in number of ballots sampled could correspond to many days of work. 
% Section~\ref{sec:workload} discusses workload in more depth.

\begin{figure}
\includegraphics[width=.5\textwidth]{prov_asn.png}
\caption{For the entire audit, consisting of all five rounds, the estimated stopping probability for average number of ballots drawn for \Providence, \Minerva, EoR \BRAVO, and SO \BRAVO.}
\label{fig:prov-asn}
\end{figure}
